---
title: "TB Preventive Treatment Cascade: Descriptive Analysis"
subtitle: "Contacts, Homeless Persons, and People Living with HIV — Vladimir, Kovrov, and Murom"
format:
  html:
    toc: true
    toc-depth: 2
    embed-resources: true
    code-fold: true
  gfm:
    output-file: descriptive_report.md
execute:
  echo: false
  warning: false
params:
  run_date: !expr as.character(Sys.Date())
  analysis_ready_path: ""
---

```{r}
#| label: setup
devtools::load_all(rprojroot::find_root(rprojroot::is_r_package, path = getwd()), quiet = TRUE)

run_date <- as.Date(params$run_date)
kable_pct <- function(df, ...) knitr::kable(df, digits = 3, ...)

git_hash <- tryCatch(
  system2("git", c("-C", repo_root(), "rev-parse", "--short", "HEAD"), stdout = TRUE),
  error = function(e) NA_character_
)

using_snapshot <- nzchar(params$analysis_ready_path)
if (using_snapshot) {
  tab <- arrow::read_parquet(params$analysis_ready_path)
  n_raw <- NA_integer_
  qc_result <- NULL
} else {
  raw <- suppressWarnings(load_raw())
  n_raw <- nrow(raw)
  qc_result <- run_qc(raw)
  tab <- build_analysis_table(raw, analysis_date = run_date)
}
n_analysis <- nrow(tab)
n_censored <- sum(tab$censored)
```

## Report metadata

| | |
|---|---|
| Snapshot / analysis date | `r format(run_date, "%Y-%m-%d")` |
| Git commit | `r ifelse(is.na(git_hash), "unavailable", git_hash)` |
| Input | `r if (using_snapshot) params$analysis_ready_path else raw_data_path()` |
| Rows ingested | `r if (using_snapshot) "n/a (pre-built snapshot)" else n_raw` |
| Rows in analysis table | `r n_analysis` |
| Rows right-censored (< `r CENSORING_WINDOW_MONTHS` months of follow-up; excluded from Steps 4/6/8 outcome-maturity analyses) | `r n_censored` |

```{r}
#| label: qc-skip-note
#| eval: !expr using_snapshot
#| results: asis
cat(
  "_This report ran against a pre-built analysis-ready snapshot, which has already passed",
  "the Section 6 QC checks below at build time. Re-render with `analysis_ready_path` unset to",
  "regenerate the QC section directly against the raw CSV._"
)
```

## Section 6 — Data management and quality control

```{r}
#| label: qc-tables
#| eval: !expr isFALSE(using_snapshot)
kable_pct(qc_result$schema_summary)
kable_pct(qc_result$check_summary)
kable_pct(qc_result$date_order_pairs)
kable_pct(qc_result$missingness$by_column)
```

No record is dropped from the analysis table as a result of these checks: flagged rows are
retained and surfaced here for transparency, per Section 6's "distinguish structural missingness
from data-entry gaps" guidance. The full per-site missingness and flagged-row detail can be
regenerated at any time via `render_qc_report(run_qc(load_raw()), path)`.

## Step 1 — Population profile (Table 1)

```{r}
#| label: step1-table1
render_table1(table1(tab, by = "Source"))
```

```{r}
#| label: step1-contacts
kable_pct(contacts_per_index_case(tab))
```

## Step 2 — Screening cascade

```{r}
#| label: step2-overall
funnel_chart(screening_cascade(tab))
```

```{r}
#| label: step2-by-target-group
funnel_chart(screening_cascade(tab, "TargetGroup"), facet_var = "TargetGroup")
```

```{r}
#| label: step2-by-site
funnel_chart(screening_cascade(tab, "Source"), facet_var = "Source")
```

## Step 3 — Diagnostic outcomes

```{r}
#| label: step3-overall
funnel_chart(diagnostic_outcomes(tab))
```

```{r}
#| label: step3-by-target-group
funnel_chart(diagnostic_outcomes(tab, "TargetGroup"), facet_var = "TargetGroup")
```

```{r}
#| label: step3-by-site
funnel_chart(diagnostic_outcomes(tab, "Source"), facet_var = "Source")
```

## Step 4 — LTI preventive treatment cascade

```{r}
#| label: step4-cascade
funnel_chart(lti_treatment_cascade(tab))
```

```{r}
#| label: step4-delay
delay <- initiation_delay_summary(tab)
kable_pct(delay$delay)
kable_pct(delay$within_target)
```

## Step 5 — Regimen description

```{r}
#| label: step5-overall
funnel_chart(regimen_composition(tab))
```

```{r}
#| label: step5-by-site
funnel_chart(regimen_composition(tab, "Source"), facet_var = "Source")
```

```{r}
#| label: step5-by-year
funnel_chart(regimen_by_year(tab), facet_var = "year")
```

## Step 6 — Adherence and completion

```{r}
#| label: step6-dose-uptake
funnel_chart(dose_threshold_uptake(tab))
```

```{r}
#| label: step6-adherence
kable_pct(adherence_summary(tab))
```

```{r}
#| label: step6-outcome-by-site
outcome_stacked_bar(outcome_breakdown(tab, "Source"), "outcome_branch", "Source")
```

```{r}
#| label: step6-outcome-by-target-group
outcome_stacked_bar(outcome_breakdown(tab, "TargetGroup"), "outcome_branch", "TargetGroup")
```

## Step 7 — Incentive payment uptake

```{r}
#| label: step7-overall
funnel_chart(incentive_uptake(tab))
```

```{r}
#| label: step7-by-site
funnel_chart(incentive_uptake(tab, "Source"), facet_var = "Source")
```

```{r}
#| label: step7-delay
kable_pct(dplyr::select(
  incentive_uptake(tab), "milestone", "median_delay_days", "delay_iqr_low", "delay_iqr_high"
))
```

## Step 8 — Follow-up and final outcomes

```{r}
#| label: step8-followup
funnel_chart(followup_outcomes(tab))
```

```{r}
#| label: step8-outcome-by-site
outcome_stacked_bar(final_outcome_distribution(tab, "Source"), "final_outcome_category", "Source")
```

```{r}
#| label: step8-outcome-by-completion
outcome_stacked_bar(
  final_outcome_distribution(tab, by_completion = TRUE),
  "final_outcome_category", "completed_or_finished"
)
```

```{r}
#| label: step8-incidence
kable_pct(incidence_rate(tab))
kable_pct(incidence_rate(tab, "Source"))
```

## Step 9 — Temporal trends

```{r}
#| label: step9-enrollment
trend_line_chart(enrollment_trends(tab))
```

```{r}
#| label: step9-by-site
trend_line_chart(quarterly_counts(tab, "DateScreening", group_vars = "Source"), color_var = "Source")
```

## Step 10 — Site comparison

```{r}
#| label: step10-site-comparison
site_comparison_table(site_comparison(tab))
```

## Limitations and disclosure control

Right-censoring, programmatic (non-randomized) data, structurally missing fields for non-contact
target groups, and site-dependent follow-up completeness all apply to every result above exactly
as described in the Study Plan's Section 10 — see that document for the full discussion. Every
stratified cell with a count below `r SMALL_CELL_THRESHOLD` is suppressed throughout this report
per Section 11's disclosure-control requirement, either by omission (charts) or by an explicit
`"<5"` marker (Step 10's table); [Table 1](#step-1-population-profile-table-1) is the one
exception, footnoted rather than suppressed, since it summarises the full cohort rather than a
cascade numerator/denominator pair.
